sWGS validation report

### 2019-08-07 Validation Report.Rmd
...

sheets = readxl::excel_sheets(val.file)[1:12]
all.val = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s) %>% select(`Hospital Research ID`, matches('Status'), `Block ID`,`Sample Type`, `SLX-ID`, `Index Sequence`, Cohort, Batch, RA, matches('Collection')) %>% dplyr::filter(!is.na(`SLX-ID`)) %>% mutate_at(vars(`SLX-ID`, `Block ID`), list(as.character)) %>% fncols('Collection', 'Biopsy')
}))

@@

val = do.call(bind_rows, lapply(list.files(analysis.dir, 'residuals', recursive = T, full.names = T), function(f) {
  readr::read_tsv(f, col_types = 'cdddddl', col_names = F) %>% set_names('sample', 'varMAD_median', 'varMAD_sd', 'varMAD_Q1', 'varMAD_Q3', 'n.segs', 'Pass')  %>% 
    mutate(`Patient ID` = as.character(basename(dirname(f))))
})) %>% select(`Patient ID`, sample, varMAD_median, n.segs) %>% mutate(varMAD_median = round(varMAD_median, 3)) %>% mutate(sample = str_replace(sample, '_', '-'))

@@

val = val %>% filter(sample %in% (all.val %>% select(Samplename) %>% pull) ) %>% 
          left_join( all.val, val %>% mutate(sample = str_replace(sample, '_', '-')), by=c('sample'='Samplename'))

@@

speedvac = left_join(val %>% ungroup %>% filter(Batch %in% c(5)), readxl::read_xlsx(val.file, sheet='Batch 5') %>% select(`Hospital Research ID`, `Block ID`, `Original Cohort`, `Speedvac`))

@@

@@

sheets = readxl::excel_sheets(val.file)[9:12]
info = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s, trim_ws = T) %>% 
    dplyr::filter(Status == 'P') %>% dplyr::select(`Hospital Research ID`, `Block ID`, Endoscopy, Pathology, `SLX-ID`, `Index Sequence`, `Path Notes`) %>% mutate(Sample = paste0(`SLX-ID`,'.',`Index Sequence`))
}))

@@

oldp.preds = oldp.preds %>% filter(Sample %in% (oldp %>% filter(!grepl('OCCAMS',`Hospital Research ID`)) %>% select(sample) %>% pull))

@@

sheets = readxl::excel_sheets(val.file)[10:12]
info = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s, trim_ws = T) %>% 
    dplyr::filter(Status == 'NP' & !is.na(`SLX-ID`)) %>% dplyr::select(`Hospital Research ID`, `Block ID`, Endoscopy, Pathology, `SLX-ID`, `Index Sequence`, `Path Notes`) %>% mutate(Sample = paste0(`SLX-ID`,'.',`Index Sequence`))
}))

@@

@@

val.new.np.preds = left_join(val %>% filter(sample %in% new.np.preds$Sample) %>% select(`Hospital Research ID`, sample, varMAD_median, n.segs, Status),
          new.np.preds %>% select(Sample, Probability, matches('Risk')), by=c('sample'='Sample'))

>>>>

sheets = readxl::excel_sheets(val.file)[1:12]
all.val = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s) %>% dplyr::select(`Hospital Research ID`, matches('Status'), `Block ID`,`Sample Type`, `SLX-ID`, `Index Sequence`, Cohort, Batch, RA, matches('Collection')) %>% dplyr::filter(!is.na(`SLX-ID`)) %>% mutate_at(vars(`SLX-ID`, `Block ID`), list(as.character)) %>% fncols('Collection', 'Biopsy')
}))

@@

val = do.call(bind_rows, lapply(list.files(analysis.dir, 'residuals', recursive = T, full.names = T), function(f) {
  readr::read_tsv(f, col_types = 'cdddddl', col_names = F) %>% set_names('sample', 'varMAD_median', 'varMAD_sd', 'varMAD_Q1', 'varMAD_Q3', 'n.segs', 'Pass')  %>% 
    mutate(`Patient ID` = as.character(basename(dirname(f))))
})) %>% dplyr::select(`Patient ID`, sample, varMAD_median, n.segs) %>% mutate(varMAD_median = round(varMAD_median, 3)) %>% mutate(sample = str_replace(sample, '_', '-'))

@@

val = val %>% filter(sample %in% (all.val %>% dplyr::select(Samplename) %>% pull) ) %>% 
          left_join( all.val, val %>% mutate(sample = str_replace(sample, '_', '-')), by=c('sample'='Samplename'))

@@

speedvac = left_join(val %>% ungroup %>% filter(Batch %in% c(5)), readxl::read_xlsx(val.file, sheet='Batch 5') %>% dplyr::select(`Hospital Research ID`, `Block ID`, `Original Cohort`, `Speedvac`))

@@

if (file.exists('batch8_preds.txt')) {
  batch8_preds = read_tsv('batch8_preds.txt')
} else {
  segFiles = grep(paste(on$`Patient ID`,collapse='|'), list.files('~/Data/BarrettsProgressionRisk/Analysis/validation', 'segObj',  full.names = T, recursive = T), value=T)

  batch8_preds = do.call(bind_rows, lapply(segFiles, function(f) {
    print(f)
    load(f)
    if (nrow(sampleResiduals(segmented)) <= 0) return()

    segmented$sample.info = loadSampleInformation(  
      on %>% filter(sample %in% segmented$sample.info$Sample) %>%
        dplyr::rename('Endoscopy' = `Sample Date`, Sample = sample ) )

    prr = BarrettsProgressionRisk::predictRiskFromSegments(segmented, F)
    BarrettsProgressionRisk::predictions(prr,'sample')
  }))
  batch8_preds = batch8_preds %>% filter(!is.na(`Patient ID`))

  write_tsv(batch8_preds, 'batch8_preds.txt')
}

batch8_preds %>% dplyr::select(`Patient ID`, Sample, everything(), -matches('Hospital|SLX|Index') ) %>% kable() %>% kable_styling('striped')

batch8_preds %>% group_by(Risk) %>% dplyr::summarise('n Samples'= length(Risk)) %>% kable(caption='Predictions') %>% kable_styling(full_width = F)

@@

sheets = readxl::excel_sheets(val.file)[9:12]
info = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s, trim_ws = T) %>% 
    dplyr::filter(Status == 'P') %>% dplyr::select(`Hospital Research ID`, `Block ID`, Endoscopy, Pathology, `SLX-ID`, `Index Sequence`, `Path Notes`) %>% dplyr::mutate(Sample = paste0(`SLX-ID`,'.',`Index Sequence`))
}))

@@

oldp.preds = left_join(oldp.preds, val %>% dplyr::select(sample, varMAD_median, n.segs), by=c('Sample'='sample'))

oldp.preds = oldp.preds %>% filter(Sample %in% (oldp %>% filter(!grepl('OCCAMS',`Hospital Research ID`)) %>% dplyr::select(sample) %>% pull))

@@

```{r}
sheets = readxl::excel_sheets(val.file)[10:12]
info = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s, trim_ws = T) %>% 
    dplyr::filter(Status == 'NP' & !is.na(`SLX-ID`)) %>% dplyr::select(`Hospital Research ID`, `Block ID`, Endoscopy, Pathology, `SLX-ID`, `Index Sequence`, `Path Notes`) %>% mutate(Sample = paste0(`SLX-ID`,'.',`Index Sequence`))
}))

@@

new.np.preds = left_join(new.np.preds, val %>% dplyr::select(sample, varMAD_median, n.segs), by=c('Sample'='sample'))

#cor.test(new.np.preds$n.segs, new.np.preds$varMAD_median)

@@

val.new.np.preds = left_join(val %>% filter(sample %in% new.np.preds$Sample) %>% dplyr::select(`Hospital Research ID`, sample, varMAD_median, n.segs, Status),
          new.np.preds %>% dplyr::select(Sample, Probability, matches('Risk')), by=c('sample'='Sample'))
